Mechanical loading prediction through accelerometry data during walking and running

### 2022-05-28 manuscript/manuscript.Rmd
Revise the manuscript

>>>>

It is also important to highlight that, during peak detection, it was observed a mismatch in the stance phase in which the pACC and pGRF are detected. This mismatch occurred particularly at running speeds, in which the pACC is roughly at 20% of the stance and the pGRF at around 50% of the stance. Nevertheless, although we have detected this mismatch, and, effectively, the pACC and pGRF that were detected do not represent the same event in the stance phase, by using the prediction method developed in this paper we could accurately predict the active pGRF at both walking and running.
